Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-11-12 paper/paper.tex
start rewriting abstract

\begin{abstract}

\end{abstract}

@@

>>>>

\begin{abstract}
Extended playing techniques such as vibratos, glissandos, and trills often denote musical expressivity, both in erudite and folk contexts.
They affect the spectrotemporal modulations of pitched audio signals, thereby modifying timbre perception systematically.
However, most existing approaches to music similarity retrieval inadequately reflect this effect, as they fail to describe timbre beyond the so-called ``ordinary'' technique; use instrument identity as a proxy for timbre quality; or do not allow for rapid customization to the perceptual idiosyncracies of a newcoming subject.
%Our article fills this gap in scholarship by providing a scalable algorithm for measuring the timbre similarity between any two audio samples
\end{abstract}

@@

%TODO VL: comment on visualization of similarity matrices.
